Linear stability of magnetized massive protoplanetary disks

### 2014-03-31 paper/linear.tex
tex update
tex updates

\section{Linear problem}\label{linear}
We consider axisymmetric Eulerian perturbations to the above
equilibrium in the form $\real[\dd\rho(z)\exp{\imgi(k_xx + \sigma
    t)}]$ and similarly for other fluid variables. Here, $k_x$ is a
constant radial wavenumber and $\sigma=-(\omega +\imgi\gamma)$ is a
complex  frequency, where $-\omega$ is the real mode frequency and $\gamma$ is
the growth rate. We take $k_x>0$ without loss of generality. 
Hereafter, we surpress the exponential factor, as
well as the real part notation.

The linearized continuity equation is 
\begin{align}
  \frac{\imgi\sigma}{c_s^2}W + \imgi k_x \dd v_x
  +\left(\ln\rho\right)^\prime\dd v_z + \dd v_z^\prime = 0,\label{lin_cont}
\end{align}
where $^\prime$ denotes $d/dz$ and $W=\delta P/\rho =
c_s^2\delta\rho/\rho$ is the enthalpy perturbation.  
The linearized equations of motion are
\begin{align}
  &\imgi\sigma \dvx - 2\Omega\dvy  = - \imgi
  k_x\w + \frac{B_z}{\mu_0\rho} \left[\dbx^\prime - \imgi 
    k_x\left(\dbz + \epsilon\dby\right)\right],\\
  &\imgi\sigma\dvy + 
    \frac{\kappa^2}{2\Omega}\dvx = \frac{B_z}{\mu_0\rho}\dby^\prime\label{lin_vy},\\ 
  & \imgi\sigma\dvz = -\w^\prime - \frac{B_y}{\mu_0\rho}\dby^\prime\label{lin_vz},  
\end{align}
where the effective enthalpy perturbation
$\w = W + \dphi$. The linearized induction equation is
\begin{align}
&  \imgi\bar{\sigma}\dbx = B_z\dvx^\prime +
  \eta\dbx^{\prime\prime}+\eta^\prime\dbx^\prime - \imgi k_x
  \eta^\prime \dbz,\label{induct_x}\\
&\imgi\bar{\sigma}\dby = B_z\dvy^\prime -B_y\Delta - S\dbx +
  \eta\dby^{\prime\prime}+\eta^\prime\dby^\prime,\label{induct_y}\\
& \imgi\bar{\sigma}\dbz = -\imgi  k_xB_z \dvx +
\eta\dbz^{\prime\prime}, \label{induct_vert}
%& \imgi\bar{\sigma}\dbz = -\imgi  k_x \dvx  -\imgi k_x\eta \dbx^{\prime}, \label{induct_vert}
\end{align} 
where $\imgi\bar{\sigma} = \imgi\sigma + \eta k_x^2$,
$\Delta\equiv \nabla\cdot\bm{\delta v}  = \imgi k_x\dvx + \dvz^\prime$,   
and the divergence-free condition is $\imgi k_x\dbx +
\dbz^\prime=0$. Finally, the linearized Poisson equation is 
\begin{align}
  \dphi^{\prime\prime} - k_x^2\dphi = \frac{\Omega^2\rho}{c_s^2Q\rho_0}W.  \label{lin_poisson}
\end{align}

We eliminate $\dd\bm{B}$ and $\dvz$ between the linearized
equations to obtain a system of ordinary differential equations for
$\bm{U}=\left(\dvx,\dvy,W,\dphi\right)$. We detail the steps 
in Appendix \ref{reduction} for two cases considered in this paper:
%We consider two cases:
\begin{enumerate}
\item Purely vertical field with constant or variable
  resistivity (see below), so that $\epsilon = 0$ and $\eta=\eta(z)$. 
\item Tilted field with uniform resistivity
  so that $\epsilon \neq 0$ and $\eta=\rm{constant}$.   
\end{enumerate}
Schematically, the numerical problem is to solve 
\begin{align}
  L_{11}\dvx + L_{12}\dvy + L_{13}W + L_{14}\dphi &= 0, \label{lin1}\\
  L_{21}\dvx + L_{22}\dvy + L_{23}W + L_{24}\dphi &= 0, \label{lin2}\\
  L_{31}\dvx +L_{32}\dvy + L_{33}W + L_{34}\dphi &=0,\label{lin3}\\
  \phantom{L_{31}\dvx + L_{22}\dvy +} L_{43}W + L_{44}\dphi
  &=0\label{lin4},
\end{align}
where differential operators $L_{1j},\,L_{2j}$ and $L_{3j}$
($j=1,2,3,4$) can be read off Appendix \ref{reduction} and $L_{4j}$
($j=3,4$) from the linearized Poisson equation above. We remark that
the more general problem of tilted field and variable resistivity
%($\epsilon\neq0$ and $\eta=\eta(z)$
can also be reduced to the above form.

@@

\subsubsection{Case 1: vertical field}
We impose $\bm{U}$ to be an even function of $z$, so that
$d\bm{U}/dz=0$ at $z=0$. This reduces the computational domain to
$z\in[0,Z_s]$ and permits higher numerical resolution. At the disk
surface we set %$\dbx=\dby=\dvz=0$ 
\begin{align}
  \dbx(Z_s) = \dby(Z_s) = \dvz (Z_s) = 0, 
\end{align}
so the field remains vertical. The potential boundary
condition is 
\begin{align}
  \dphi^\prime(\zmax) + k_x\dphi(\zmax) = 0 \label{pot_bc1}
\end{align}
\citep{goldreich65a}.

@@

\subsection{Numerical procedure}
We use a pseudo-spectral method to solve the set of linearized
equations. Let
\begin{align}\label{cheby_expand}
  \bm{U}(z) 
  = \sum_{k=1}^{N_z} \bm{U}_k\psi_k(z/\zmax), 
\end{align}
where 
\begin{align}
  \psi_k  = 
  \begin{cases}
    T_{2(k-1)} & B_y \equiv 0 \text{ (case 1)},\\
    T_{k-1}   & B_y\neq 0 \text{ (case 2)},
  \end{cases}
\end{align}
and  $T_l$ is a Chebyshev polynomial of the first kind of order $l$
\citep{stegun65}. Note that for case 1 the midplane symmetry condition
is taken care of by the choice of basis functions. 
%Note that in case 1
%The number of basis functions is
%$N_z$ and $l_\mathrm{max}=2(N_Z-1)$ is the highest polynomial order. 
%For a vertical field we only use even Chebyshev polynomials 
%to satisfy the symmetry condition at $z=0$, so in case 1 we only
%consider $z\geq 0$.

The pseudo-spectral coefficients $\bm{U}_n$  are obtained by demanding
the set of linear equations to be satisfied at $N_z$ collocation
points along the vertical direction. We choose these points as the
extrema of $T_{l_\mathrm{max}}$ plus end points, where
$l_\mathrm{max}$ is the highest polynomial order. Our standard
resolution is $N_z=256$.

The above procedure discretizes the linear equations to a matrix equation,
\begin{align}\label{matrix_eqn}
\bm{M}\bm{w} = 0, 
\end{align}
where $\bm{M}$ is a $4N_z\times 4 N_z$ matrix representing the $L_{ij}$ 
and upper disk boundary conditions, 
and $\bm{w}$ is a vector storing the pseudo-spectral coefficients. 
Starting with an initial guess for $\sigma$, non-trivial solutions to
Eq. \ref{matrix_eqn} are obtained by varying $\sigma$ using Newton-Raphson iteration 
such that $\mathrm{det}\bm{M}=0$ \citep[details can be found in][]{lin12}.

@@

\subsection{Diagnostics}
We visualize results in terms of dimensionless energy densities. We
define 
\begin{align}
  &E_m \equiv \frac{|\delta \hat{\bm{B}}|^2}{2\beta},\\
  &E_g =
  \frac{\hat{\rho}}{\hat{c}_s^2}\left|\real\left(\hat{W}\dd\hat{\Phi}^*\right)\right|,\\  
  &E_k = \frac{1}{2}\hat{\rho}|\delta\hat{\bm{v}}|^2,\\
  &E_t = \frac{\hat{\rho}|\hat{W}|^2}{2\hat{c}_s^2},
\end{align}
as the perturbed magnetic, gravitational, kinetic and thermal
energies, respectively, which are functions of $z$. The total energy
is $E=E_m+E_g+E_k+E_t$. We use $\avg{\cdot}$ to denote an average over
$z$. 
%and we then normalize $E_i$ by
%$\mathrm{max}(E)$.

>>>>

\section{Linear problem}\label{linear}
We consider axisymmetric Eulerian perturbations to the above
equilibrium in the form $\real[\dd\rho(z)\exp{\imgi(k_xx + \sigma
    t)}]$ and similarly for other fluid variables. Here, $k_x$ is a
constant radial wavenumber and $\sigma=-(\omega +\imgi\gamma)$ is a
complex  frequency, where $-\omega$ is the real mode frequency and $\gamma$ is
the growth rate. We take $k_x>0$ without loss of generality. 
Hereafter, we surpress the exponential factor and the real part notation.

The linearized continuity equation is 
\begin{align}
  \frac{\imgi\sigma}{c_s^2}W + \imgi k_x \dd v_x
  +\left(\ln\rho\right)^\prime\dd v_z + \dd v_z^\prime = 0,\label{lin_cont}
\end{align}
where $^\prime$ denotes $d/dz$ and $W=\delta P/\rho =
c_s^2\delta\rho/\rho$ is the enthalpy perturbation.  
The linearized equations of motion are
\begin{align}
  &\imgi\sigma \dvx - 2\Omega\dvy  = - \imgi
  k_x\w + \frac{B_z}{\mu_0\rho} \left[\dbx^\prime - \imgi 
    k_x\left(\dbz + \epsilon\dby\right)\right],\\
  &\imgi\sigma\dvy + 
    \frac{\kappa^2}{2\Omega}\dvx = \frac{B_z}{\mu_0\rho}\dby^\prime\label{lin_vy},\\ 
  & \imgi\sigma\dvz = -\w^\prime - \frac{B_y}{\mu_0\rho}\dby^\prime\label{lin_vz},  
\end{align}
where the effective enthalpy perturbation
$\w = W + \dphi$. The components of the linearized induction equation
are 
\begin{align}
&  \imgi\bar{\sigma}\dbx = B_z\dvx^\prime +
  \eta\dbx^{\prime\prime}+\eta^\prime\dbx^\prime - \imgi k_x
  \eta^\prime \dbz,\label{induct_x}\\
&\imgi\bar{\sigma}\dby = B_z\dvy^\prime -B_y\Delta - S\dbx +
  \eta\dby^{\prime\prime}+\eta^\prime\dby^\prime,\label{induct_y}\\
& \imgi\bar{\sigma}\dbz = -\imgi  k_xB_z \dvx +
\eta\dbz^{\prime\prime}, \label{induct_vert}
%& \imgi\bar{\sigma}\dbz = -\imgi  k_x \dvx  -\imgi k_x\eta \dbx^{\prime}, \label{induct_vert}
\end{align} 
where $\imgi\bar{\sigma} = \imgi\sigma + \eta k_x^2$,
$\Delta\equiv \nabla\cdot\bm{\delta v}  = \imgi k_x\dvx + \dvz^\prime$,   
and the divergence-free condition is $\imgi k_x\dbx +
\dbz^\prime=0$. Finally, the linearized Poisson equation is 
\begin{align}
  \dphi^{\prime\prime} - k_x^2\dphi = \frac{\Omega^2\rho}{c_s^2Q\rho_0}W.  \label{lin_poisson}
\end{align}

We eliminate $\dd\bm{B}$ and $\dvz$ between the linearized
equations to obtain a system of ordinary differential equations for
$\bm{U}=\left(\dvx,\dvy,W,\dphi\right)$. We detail the steps 
in Appendix \ref{reduction} for two cases considered in this paper:
%We consider two cases:
\begin{enumerate}
\item Purely vertical field with constant or variable
  resistivity, so that $\epsilon = 0$ and $\eta=\eta(z)$. 
\item Tilted field with uniform resistivity
  so that $\epsilon \neq 0$ and $\eta=\rm{constant}$.   
\end{enumerate}
Schematically, the numerical problem is to solve 
\begin{align}
  L_{11}\dvx + L_{12}\dvy + L_{13}W + L_{14}\dphi &= 0, \label{lin1}\\
  L_{21}\dvx + L_{22}\dvy + L_{23}W + L_{24}\dphi &= 0, \label{lin2}\\
  L_{31}\dvx +L_{32}\dvy + L_{33}W + L_{34}\dphi &=0,\label{lin3}\\
  \phantom{L_{31}\dvx + L_{22}\dvy +} L_{43}W + L_{44}\dphi
  &=0\label{lin4},
\end{align}
where the differential operators $L_{1j},\,L_{2j}$ and $L_{3j}$
($j=1,2,3,4$) can be read off Appendix \ref{reduction} and $L_{4j}$
($j=3,4$) from the linearized Poisson equation above. We remark that
the case of a tilted field and variable resistivity
%($\epsilon\neq0$ and $\eta=\eta(z)$
can also be reduced to the above form.

@@

\subsubsection{Case 1: vertical field}%because SG can only destabilize
                                %symmetric density perts
We impose $\bm{U}$ to be an even function of $z$, so that
$d\bm{U}/dz=0$ at $z=0$. This reduces the computational domain to
$z\in[0,Z_s]$ and permits higher numerical resolution. At the disk
surface we set %$\dbx=\dby=\dvz=0$ 
\begin{align}
  \dbx(Z_s) = \dby(Z_s) = \dvz (Z_s) = 0, 
\end{align}
so the field remains vertical. The potential boundary
condition is 
\begin{align}
  \dphi^\prime(\zmax) + k_x\dphi(\zmax) = 0 \label{pot_bc1},
\end{align}
and is adapted from \cite{goldreich65a}. The general form of this
potential boundary condition is used for case 2 below.

@@

\subsection{Numerical procedure}
We use a pseudo-spectral method to solve the set of linearized
equations. Let
\begin{align}\label{cheby_expand}
  \bm{U}(z) 
  = \sum_{k=1}^{N_z} \bm{U}_k\psi_k(z/\zmax), 
\end{align}
where 
\begin{align}
  \psi_k  = 
  \begin{cases}
    T_{2(k-1)} & B_y \equiv 0 \text{ (case 1)},\\
    T_{k-1}   & B_y\neq 0 \text{ (case 2)},
  \end{cases}
\end{align}
and  $T_l$ is a Chebyshev polynomial of the first kind of order $l$
\citep{stegun65}. Note that for case 1 the mid-plane symmetry condition
is taken care of by the choice of basis functions. 
%Note that in case 1
%The number of basis functions is
%$N_z$ and $l_\mathrm{max}=2(N_Z-1)$ is the highest polynomial order. 
%For a vertical field we only use even Chebyshev polynomials 
%to satisfy the symmetry condition at $z=0$, so in case 1 we only
%consider $z\geq 0$.

The pseudo-spectral coefficients $\bm{U}_n$  are obtained by demanding
the set of linear equations to be satisfied at $N_z$ collocation
points along the vertical direction. We choose these points as the
extrema of $T_{l_\mathrm{max}}$ plus end points, where
$l_\mathrm{max}$ is the highest polynomial order. Our standard
resolution is $N_z=256$ ($N_z=257$) for case 1 (case 2).

The above procedure discretizes the linear equations to a matrix equation,
\begin{align}\label{matrix_eqn}
\bm{M}\bm{w} = \mathbf{0}, 
\end{align}
where $\bm{M}$ is a $4N_z\times 4 N_z$ matrix representing the $L_{ij}$ 
plus boundary conditions, 
and $\bm{w}$ is a vector storing the pseudo-spectral coefficients. 
Starting with an initial guess for $\sigma$, non-trivial solutions to
Eq. \ref{matrix_eqn} are obtained by varying $\sigma$ using Newton-Raphson iteration 
such that $\mathrm{det}\bm{M}=0$ \citep[details can be found in][]{lin12}.

@@

\subsection{Diagnostics}
We visualize results in terms of dimensionless energy densities. We
define 
\begin{align}
  &E_m \equiv \frac{|\delta \hat{\bm{B}}|^2}{2\beta},\\
  &E_g = 
  \frac{\hat{\rho}}{2\hat{c}_s^2}\left|\real\left(\hat{W}\dd\hat{\Phi}^*\right)\right|,\\  
  &E_k = \frac{1}{2}\hat{\rho}|\delta\hat{\bm{v}}|^2,\\
  &E_t = \frac{\hat{\rho}|\hat{W}|^2}{2\hat{c}_s^2},
\end{align}
as the perturbed magnetic, gravitational, kinetic and thermal
energies, respectively, which are functions of $z$. Although we do not
solve an energy equation, we nevertheless define $E_t$ as a measure of
density perturbations \citep{kojima89}. The total energy
is $E=E_m+E_g+E_k+E_t$. We use $\avg{\cdot}$ to denote an average over
$z$. 
%The colorbar quantifies the importance of
%self-gravity with

Since we will primarily be concerned with massive disks, we define
\begin{align}
 \tau \equiv \frac{\avg{E_g}}{\avg{E_g} + \avg{E_m}} 
\end{align} 
as a measure of the importance of self-gravity. Thus, modes with $\tau
= 1$ are energetically dominated by self-gravity (GI) and modes with
$\tau\ll1$ are dominated by magnetic perturbations (MRI).

%and we then normalize $E_i$ by
%$\mathrm{max}(E)$.

### 2014-03-31 paper/paper.tex
tex updates

\usepackage{amsmath}
%\usepackage{url}
\usepackage{bm}
%\usepackage[font=small,format=plain,labelfont=bf,up,textfont=it,up]{caption}
\newcommand{\p}{\partial}
\newcommand{\lmax}{l_\mathrm{max}}
\newcommand{\sbar}{\bar{\sigma}} 
\newcommand{\imgi}{\mathrm{i}} 
\newcommand{\ii}{\mathrm{i}}
\newcommand{\C}{\mathcal{C}^\lambda}
\newcommand{\wop}[1]{\mathcal{V}^{(#1)}}
\newcommand{\avg}[1]{\langle{#1}\rangle}
\newcommand{\zhat}{\hat{z}}
\newcommand{\rhat}{\hat{r}}
\newcommand{\he}{\mathcal{H}}
\newcommand{\amp}{\mathcal{A}}
\newcommand{\dd}{\delta}
\newcommand{\real}{\operatorname{Re}}
\newcommand{\imag}{\operatorname{Im}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\zmax}{Z_s}
\newcommand{\wbar}{\tilde{W}}
\newcommand{\qbar}{\tilde{Q}}
\newcommand{\dbigH}{\frac{H^\prime}{H}}
\newcommand{\Rp}{\frac{\rho_0^\prime}{\rho_0}}
\newcommand{\Fp}{\frac{g^\prime}{g}}
\newcommand{\Rpp}{\frac{\rho_0^{\prime\prime}}{\rho_0}}
\newcommand{\Fpp}{\frac{g^{\prime\prime}}{g}}
\newcommand{\ils}{L_s^{-1}}
\newcommand{\ilp}{L_p^{-1}}
\newcommand{\ihp}{H_p^{-1}}
\newcommand{\ihs}{H_s^{-1}}
\newcommand{\ciso}{c_\mathrm{iso}}
\newcommand{\csmid}{c_{s0}} 
\newcommand{\hiso}{h_\mathrm{iso}}
\newcommand{\Hiso}{H_\mathrm{iso}}
\newcommand{\zeus}{\texttt{ZEUS-MP }}
\newcommand{\rsph}{r_\mathrm{sph}}
\newcommand{\dvx}{\dd v_x}
\newcommand{\dvy}{\dd v_y}
\newcommand{\dvz}{\dd v_z}
\newcommand{\dbx}{\dd B_x}
\newcommand{\dby}{\dd B_y}
\newcommand{\dbz}{\dd B_z}
\newcommand{\w}{ \widetilde{W}}
%\newcommand{\sbar}{\bar{\sigma}}
\newcommand{\dphi}{\dd \Phi}
\newcommand{\actaa}{Acta Astron.}
\defcitealias{lin12}{L12}

@@

\begin{abstract}
  Magneto-rotational instability (MRI) and gravitational instability
  (GI) are the two principle routes to turbulent angular momentum
  transport in accretion disks. Protoplanetary disks may develop
  both. The goal of this paper is to reinvigorate interest in the study of
  magnetized  massive protoplanetary disks, starting from the basic
  issue of stability. The linear stability of a local patch of a
  self-gravitating, magnetized three-dimensional (3D) disk to
  axisymmetric perturbations is examined. %Addition effects such as
  %resistivity and azimuthal fields are considered.

%We examine the local linear stability of
%  magnetized, self-gravitating and differentially rotating disks to
%  axisymmetric perturbations. 
%
%not many studies model both
%revisits 
\end{abstract}

>>>>

\usepackage{amsmath}
%\usepackage{url}
\usepackage{bm}
%\usepackage[font=small,format=plain,labelfont=bf,up,textfont=it,up]{caption}
\newcommand{\p}{\partial}
\newcommand{\lmax}{l_\mathrm{max}}
\newcommand{\sbar}{\bar{\sigma}} 
\newcommand{\imgi}{\mathrm{i}} 
\newcommand{\ii}{\mathrm{i}}
\newcommand{\C}{\mathcal{C}^\lambda}
\newcommand{\wop}[1]{\mathcal{V}^{(#1)}}
\newcommand{\avg}[1]{\langle{#1}\rangle}
%\newcommand{\max}[1]{\mathrm{max}({#1})}
%\newcommand{\min}[1]{\mathrm{min}({#1})}
\newcommand{\zhat}{\hat{z}}
\newcommand{\rhat}{\hat{r}}
\newcommand{\he}{\mathcal{H}}
\newcommand{\amp}{\mathcal{A}}
\newcommand{\dd}{\delta}
\newcommand{\real}{\operatorname{Re}}
\newcommand{\imag}{\operatorname{Im}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\zmax}{Z_s}
\newcommand{\wbar}{\tilde{W}}
\newcommand{\qbar}{\tilde{Q}}
\newcommand{\dbigH}{\frac{H^\prime}{H}}
\newcommand{\Rp}{\frac{\rho_0^\prime}{\rho_0}}
\newcommand{\Fp}{\frac{g^\prime}{g}}
\newcommand{\Rpp}{\frac{\rho_0^{\prime\prime}}{\rho_0}}
\newcommand{\Fpp}{\frac{g^{\prime\prime}}{g}}
\newcommand{\ils}{L_s^{-1}}
\newcommand{\ilp}{L_p^{-1}}
\newcommand{\ihp}{H_p^{-1}}
\newcommand{\ihs}{H_s^{-1}}
\newcommand{\ciso}{c_\mathrm{iso}}
\newcommand{\csmid}{c_{s0}} 
\newcommand{\hiso}{h_\mathrm{iso}}
\newcommand{\Hiso}{H_\mathrm{iso}}
\newcommand{\zeus}{\texttt{ZEUS-MP }}
\newcommand{\rsph}{r_\mathrm{sph}}
\newcommand{\dvx}{\dd v_x}
\newcommand{\dvy}{\dd v_y}
\newcommand{\dvz}{\dd v_z}
\newcommand{\dbx}{\dd B_x}
\newcommand{\dby}{\dd B_y}
\newcommand{\dbz}{\dd B_z}
\newcommand{\w}{ \widetilde{W}}
%\newcommand{\sbar}{\bar{\sigma}}
\newcommand{\dphi}{\dd \Phi}
\newcommand{\actaa}{Acta Astron.}
\defcitealias{lin12}{L12}

@@

\begin{abstract}
  Magneto-rotational instability (MRI) and gravitational instability
  (GI) are the two principle routes to turbulent angular momentum
  transport in accretion disks. Protoplanetary disks may develop 
  both. This paper aims to reinvigorate interest in the study of
  magnetized  massive protoplanetary disks, starting from the basic
  issue of stability. The local linear stability of a 
  self-gravitating, uniformly magnetized, differentially rotating, 
  three-dimensional disk subject to axisymmetric perturbations is
  calculated numerically. The formulation includes 
  resistivity. It is found that the reduction in the disk scale height
  by self-gravity (SG) can decrease MRI growth rates. SG causes the MRI to
  become global in the vertical direction, and MRI modes
  with small radial lengthscales are stabilized. In massive
  disks with layered resistivity, the MRI is not well-localized
  to regions where the Elsasser number exceeds unity. For MRI modes
  with radial lengthscales on the order of the disk scale-height, SG
  can enhance density perturbations, an effect that becomes 
  significant in the presence of a strong toroidal field. In
  gravitationally unstable disks where GI and MRI growth rates are
  comparable, the character of unstable modes can transition smoothly
  between MRI and GI. Implications for non-linear simulations are
  discussed briefly.

%layered dis   
  %Addition effects such as
  %resistivity and azimuthal fields are considered. 
%We examine the local linear stability of
%  magnetized, self-gravitating and differentially rotating disks to
%  axisymmetric perturbations. 
%
%not many studies model both
%revisits 
\end{abstract}
